My title

### 2022-02-27 outputs/paper/paper.Rmd
Comparison with least and most affected countries

sa_data <- read_csv(here::here("inputs/data/south-africa-population-2022-02-26.csv"))
sa_data$date <- as.Date(sa_data$date)
str(sa_data)
```

@@

china <- ggplot(china_data,aes(x=date,y= `Births per 1000 People`)) + 
   labs(title = "China",
        x = "Year",
        y = "Births per 1000 People ") +
  theme_minimal() +
  geom_line()

japan <- ggplot(japan_data,aes(x=date,y= Births.per.1000.People)) + 
   labs(title = "Japan",
        x = "Year",
        y = "Births per 1000 People ") +
  theme_minimal() +
  geom_line()

us <- ggplot(us_data,aes(x=date,y= `Births per 1000 People`)) + 
   labs(title = "The United States",
        x = "Year",
        y = "Births per 1000 People ") +
  theme_minimal() +
  geom_line()

@@

```{r, include=FALSE}
#importing the Birth Rate 1950-2022 of the most affected countries: Ukraine, Argentina, Hungary, and Poland from https://www.macrotrends.net/countries/USA/united-states/birth-rate
#Then modify the 'date' variable of each into Date format for graphs by using as.Date
ukraine_data <- read_csv(here::here("inputs/data/ukraine-population-2022-02-26.csv"))
ukraine_data$date <- as.Date(ukraine_data$date)
str(ukraine_data)

@@

poland_data <- read_csv(here::here("inputs/data/poland-population-2022-02-26.csv"))
poland_data$date <- as.Date(poland_data$date)

@@

```{r, echo=FALSE}
#Generating time series graphs of births per 1000 people for each most affected country
ukraine <- ggplot(ukraine_data,aes(x=date,y= `Births per 1000 People`)) + 
   labs(title = "Ukraine",
        x = "Year",
        y = "Births per 1000 People ") +
  theme_minimal() +
  geom_line()

>>>>

sa_data <- read_csv(here::here("inputs/data/south-africa-population-2022-02-26.csv"))
sa_data$date <- as.Date(sa_data$date)
str(sa_data)

@@

china <- ggplot(china_data,aes(x=date,y= `Births per 1000 People`)) +

   labs(title = "China",
        x = "Year",
        y = "Births per 1000 People ") +
  theme_minimal() +
  geom_line()

japan <- ggplot(japan_data,aes(x=date,y= Births.per.1000.People)) +

   labs(title = "Japan",
        x = "Year",
        y = "Births per 1000 People ") +
  theme_minimal() +
  geom_line()

us <- ggplot(us_data,aes(x=date,y= `Births per 1000 People`)) +

   labs(title = "The United States",
        x = "Year",
        y = "Births per 1000 People ") +
  theme_minimal() +
  geom_line()

@@

```{r, include=FALSE}
#importing the Birth Rate 1950-2022 of the most affected countries: Ukraine, Argentina, Hungary, and Poland from https://www.macrotrends.net/countries/USA/united-states/birth-rate
#Then modify the 'date' variable of each into Date format for graphs by using as.Date

ukraine_data <- read_csv(here::here("inputs/data/ukraine-population-2022-02-26.csv"))
ukraine_data$date <- as.Date(ukraine_data$date)
str(ukraine_data)

@@

poland_data <- read_csv(here::here("inputs/data/poland-population-2022-02-26.csv"))

poland_data$date <- as.Date(poland_data$date)

@@

```{r, echo=FALSE}
#Generating time series graphs of births per 1000 people for each most affected country

ukraine <- ggplot(ukraine_data,aes(x=date,y= `Births per 1000 People`)) + 
   labs(title = "Ukraine",
        x = "Year",
        y = "Births per 1000 People ") +
  theme_minimal() +
  geom_line()
